\documentclass[../report.tex]{subfiles}
\begin{document}
\graphicspath{{img/}{../img/}}
Ubiquitous computing is an area of computer science. Coined by Mark Weiser in the early nineties, ubiquitous computing is the vision of weaving technology into the fabric of everyday life. Context-awareness is a cornerstone of ubiquitous computing. It brings situational information from the physical environment, the real world, into applications which is essential for realizing ubiquitous computers. This project presents a framework for aiding developers in making context-aware applications.

\section{Project description}
A Context-aware system is able to adapt its behavior to its surroundings. In order to act upon its environment, the system will need sensor-input. Various sources of input can be used to determine the actions of the system.

In this project we want to mainly focus on implementing a context-awareness framework, making it easy for systems to actuate on sensor events. As a proof of concept we will explore replacing the physical Scrum board, which is often a whiteboard and post-its, with an IT-solution which is not confined to a personal computer, but has the same presence. The digital Scrum board will be context-aware to the extent that it can recognize different Scrum activities, like sprint meeting or one-on-one-meeting, and automatically change its graphical interface.


\section{Scope of this project}
\label{scope}

As per our Project description there are two artefacts to be made; The context awareness framework and a proof of concept implementation in form of a Context-aware Scrum board.

\paragraph{The Framework.} 
Our project description dictates that the main piece of work will be our framework, and so implementation of this framework will have the broadest scope.\\

\begin{itemize}
\item[\textbf{Goal 1}] \textit{Our aim is to implement a framework that is adaptable and easy to use.}
\end{itemize}


\paragraph{The Scrum board.} 
For us to prove usability of the framework developed we will implement it for a context-aware Scrum board. The function of this artifact is solely to test the usefulness of the context-awareness framework.\\

\begin{itemize}
\item[\textbf{Goal 2}] \textit{In trying to prove Goal 1, implement a stub Scrum board utilizing the framework}
\end{itemize}

It is not in our scope to implement a functional or useful Scrum board.

\section{Report structure}

To best describe the intended framework, the background theory used, the choices made when designing and implementing, and the proof of concept using it, this project report will contain following main chapters.

\begin{enumerate}
\item Introduction
\item Background research
\item Design
\item Implementation
\item Proof of concept
\item Future works
\item Conclusion
\end{enumerate}
\end{document}